Unified Convergence Analysis of FedAve on Non-IID Data

### 2020-04-18 source/sec_theorems.tex
gradi dis

\begin{definition}[Gradient Dissimilarity]
	We indicate the following quantity as weighted gradient diversity among the local 
	objectives:
	\begin{align*}
		\frac{\sum_{k=1}^K p_k \left\|\nabla F_{k}\left(\mathbf{w}\right)\right\|^{2} }{\left\|   \nabla F\left(\mathbf{w}\right)\right\|^{2} } \leq \lambda 
	\end{align*}
\end{definition}

>>>>

\begin{definition}[Gradient Dissimilarity~\cite{li2018federated}]
	We indicate the following quantity as gradient diversity among the local 
	objectives:
	\begin{align*}
		\frac{\sum_{k=1}^K p_k \left\|\nabla F_{k}\left(\mathbf{w}\right)\right\|^{2} }{\left\|   \nabla F\left(\mathbf{w}\right)\right\|^{2} } \leq \lambda 
	\end{align*}
	For some $\epsilon>0$, for all the points $\vw \in \mathcal{S}_{\epsilon}^{c}=\left\{\vw |\|\nabla F(\vw)\|^{2}>\epsilon\right\}$
\end{definition}
